\section{Question 5: Change(s) of opinion}

\paragraph{Alyx Hamilton} % (fold)
\label{par:Alyx Hamilton}
The evidence provided for the first report, while not definitive, appeared to indicate the possible guilt of Alyx Hamilton regarding the disposal of the laptop. Browsing history containing job openings, correspondence with colleagues expressing discontent with the founder and CEO, David Caelus, and the cryptic email sen to \texttt{johndavis5891@gmail.com} painted a picture of a possibly disgruntled employee looking to trade the company's secrets for a better opportunity. However, I was never fully convinced of this conclusion, as a significant driving force behind it was the human impulse to draw conclusions, even with the absence of conclusive evidence.
% paragraph Alyx Hamilton (end)

\paragraph{Michael Harris} % (fold)
\label{par:Michael Harris}
The introduction of new evidence Michael Harris introduced a twist to the initial narrative. The entry and exit logs from the building gates were especially significant; it shed a light on and corroborated a piece of evidence that I had initially overlooked, and that is the correspondence between Alyx Hamilton and Sarah Jenskins. The two pieces of evidence suggested that Alyx Hamilton may not be within the premises when the initial email message sent from her address to \texttt{johndavis5891@gmail.com} was sent, nor is she likely to be engaged with her email correspondence when out on lunch with her colleague. This, alongside evidence of correspondence between Michael Harris and \texttt{johndavis5891@gmail.com} and "John Davis" on LinkedIn, prompted me to investigate the possibility of the misuse of Alyx Hamilton's laptop by Michael Harris, which then led me to checking the SAM hive on the disk image of Alyx Hamilton's laptop and discovering that the laptop was not password protected.
% paragraph Michael Harris (end)

\paragraph{Conclusion} % (fold)
\label{par:Conclusion}
While I was initally somewhat convinced of Alyx Hamilton's guilt in the disposal of the laptop, the new evidence provided made me far less certain of it.
% paragraph Conclusion (end)
