\section{Introduction} % (fold)
\label{sec:introduction}

\subsection{Background} % (fold)
\label{sub:background}

\begin{myenum}
    \item Jim's Forensics (JF) have been engaged by Penelope Legal (PL) in relation to proceedings with Caelus Engineering (CE).
    \item On the $14^\text{th}$ of September, 2021, PL instructed JF by letter containing a series of instructions on which we were to proceed.
\end{myenum}

% subsection Background (end)

\subsection{My instructions} % (fold)
\label{sub:my_instructions}

\begin{myenum}
\item As a result of the above engagement, on the $14^\text{th}$ of September, 2021, PL advised me to prepare a report addressing the following issues:
    \begin{enumerate}
        \item \textbf{Question 1 -} Does the data on the laptop provide any indications regarding the reason for its destruction and disposal? If so, what?
        \item \textbf{Question 2 -} Is there any indication of an attempt to "cover tracks", such as deleting or obscuring data?
        \item \textbf{Question 3 - } Is there any indication of hidden data, \emph{i.e.,} encryption? If so, are you able to make the data usable?
        \item \textbf{Question 4 - } Any other matters that are relevant to the use or misuse of the laptop?
        \item \textbf{Question 5 - } Has the additional information changed opinions on the events which occurred?
        \item \textbf{Question 6 - } Your recommendation regarding any further enquiries and examinations that needed to be conducted.
    \end{enumerate}
\end{myenum}

% subsection My instructions (end)

\subsection{Provided materials} % (fold)
\begin{myenum}
     \item We are provided the following materials from which we are to base our investigations on:
         \begin{enumerate}
            \item a raw image of the hard disk of Alyx Hamilton's laptop,
            \item a photo of the collection site, and 
            \item profiles of the staff at Caelus Engineering.
         \end{enumerate}
\end{myenum}
\label{sub:provided_materials}

% subsection Provided materials (end)

\subsection{Qualifications} % (fold)
\begin{myenum}
     \item I am a second year computer science student at the University of New South Wales, currently enrolled in the COMP6845 course, otherwise known as \emph{Extended Digital Forensics}.
\end{myenum}
\label{sub:qualifications}

% subsection Qualifications (end)

\subsection{Information relied upon} % (fold)
\label{sub:information_relied_upon}

\begin{myenum}
     \item I have relied upon the following information in the preparation of my report:
         \begin{enumerate}
            \item a letter containing instructions addressed to JF dated $14^\text{th}$ of September, 2021,
            \item a second letter containing further instructions addressed to JF,
            \item an image of the storage of the laptop used by Alyx Hamilton,
            \item a dump of the memory of the laptop used by Alyx Hamilton,
            \item copies of the logs of the email correspondence of Alyx Hamilton and Michael Harris,
            \item a copy of the network traffic capture data from Alyx Hamilton's laptop, as well as a log of the TLS keys necessary to decrypt the data,
            \item a screenshot of the CCTV overlooking the entry gates at Caelus Engineering,
            \item a copy of the logs of the entry and exit of personnel from the gates at Caelus Engineering,
            \item a photo of the collection site, and 
            \item profiles of the staff at Caelus Engineering.
         \end{enumerate}
\end{myenum}

% subsection Information relied upon (end)

\subsection{Disclaimer} % (fold)
\begin{myenum}
     \item I have made all inquiries which I believe are desirable and appropriate for the purposes of this report. There are no matters of significance which I regard as relevant to my opinions which have been withheld.
     \item This report has been prepared solely for the use of PL. In accordance with the usual practice of JF, I expressly disclaim all responsibility to any other person or entity (other than the Court) for any reliance on the content of this report. This report should not be copied or distributed to any other person or entity, other than in connection with the above matter.
\end{myenum}
\label{sub:disclaimer}

% subsection Disclaimer (end)

\subsection{Assumptions} % (fold)
\begin{myenum}
     
     \item In preparing this report, I have made the following assumptions:
         \begin{enumerate}
            \item the information described in the background section above is accurate, and 
            \item the computers identified by CE, and subsequently imaged, were used by Alyx Hamilton.
         \end{enumerate}
\end{myenum}
\label{sub:assumptions}

% subsection Assumptions (end)

\subsection{Structure of this report} % (fold)
\begin{myenum}
     \item The remaining sections of this report addresses the following:
         \begin{enumerate}
            \item In Section 2, I set out information with respect to Question 1 above;
            \item In Section 3, I set out information with respect to Question 2 above;
            \item In Section 4, I set out information with respect to Question 3 above;
            \item In Section 5, I set out information with respect to Question 4 above;
            \item In Section 6, I set out information with respect to Question 5 above;
            \item In Section 7, I set out information with respect to Question 6 above;
         \end{enumerate}
     \item For convenience, I note that I have organised my findings in the same order as the questions outlined in my letter of instruction. I have also included questions, in some instances paraphrased, from the letter of instruction before presenting my corresponding findings. Additionally, I have referred to the appropriate section number as contained in the letter of instruction in my responses.
\end{myenum}
\label{sub:structure_of_this_report}

% subsection Structure of this report (end)

% section Introduction (end)

% paragraph  (end)
% section Background (end)
