\section{Introduction} % (fold)
\label{sec:introduction}

\subsection{Background} % (fold)
\label{sub:background}

\begin{myenum}
    \item Jim's Forensics (JF) have been engaged by Penelope Legal (PL) in relation to proceedings with Caelus Engineering (CE).
    \item On the $14^\text{th}$ of September, 2021, PL instructed JF by letter containing a series of instructions on which we were to proceed.
\end{myenum}

% subsection Background (end)

\subsection{My instructions} % (fold)
\label{sub:my_instructions}

\begin{myenum}
\item As a result of the above engagement, on the $14^\text{th}$ of September, 2021, PL advised me to prepare a report addressing the following issues:
    \begin{enumerate}
        \item \textbf{Question 1 -} Does the data on the laptop provide any indications regarding the reason for its destruction and disposal? If so, what?
        \item \textbf{Question 2 -} Is there any indication of an attempt to "cover tracks", such as deleting or obscuring data?
        \item \textbf{Question 3 - } What additional sources would you want which would aid you in your investigation
    \end{enumerate}
\end{myenum}

% subsection My instructions (end)

\subsection{Provided materials} % (fold)
\begin{myenum}
     \item We are provided the following materials from which we are to base our investigations on:
         \begin{enumerate}
            \item a raw image of the hard disk of Alyx Hamilton's laptop,
            \item a photo of the collection site, and 
            \item profiles of the staff at Caelus Engineering.
         \end{enumerate}
\end{myenum}
\label{sub:provided_materials}

% subsection Provided materials (end)

\subsection{Qualifications} % (fold)
\begin{myenum}
     \item I am a second year computer science student at the University of New South Wales, currently enrolled in the COMP6845 course, otherwise known as \emph{Extended Digital Forensics}.
\end{myenum}
\label{sub:qualifications}

% subsection Qualifications (end)

\subsection{Information relied upon} % (fold)
\label{sub:information_relied_upon}

\begin{myenum}
     \item I have relied upon the following information in the preparation of my report:
         \begin{enumerate}
            \item a letter containing instructions addressed to JF dated $14^\text{th}$ of September, 2021,
            \item the forensic image of the laptop used by Alyx Hamilton,
            \item a photo of the collection site, and 
            \item profiles of the staff at Caelus Engineering.
         \end{enumerate}
\end{myenum}

% subsection Information relied upon (end)

\subsection{Disclaimer} % (fold)
\begin{myenum}
     \item I have made all inquiries which I believe are desirable and appropriate for the purposes of this report. There are no matters of significance which I regard as relevant to my opinions which have been withheld.
     \item This report has been prepared solely for the use of PL. In accordance with the usual practice of JF, I expressly disclaim all responsibility to any other person or entity (other than the Court) for any reliance on the content of this report. This report should not be copied or distributed to any other person or entity, other than in connection with the above matter.
\end{myenum}
\label{sub:disclaimer}

% subsection Disclaimer (end)

\subsection{Assumptions} % (fold)
\begin{myenum}
     
     \item In preparing this report, I have made the following assumptions:
         \begin{enumerate}
            \item the information described in the background section above is accurate, and 
            \item the computers identified by CE, and subsequently imaged, were used by Alyx Hamilton.
         \end{enumerate}
\end{myenum}
\label{sub:assumptions}

% subsection Assumptions (end)

\subsection{Structure of this report} % (fold)
\begin{myenum}
     \item The remaining sections of this report addresses the following:
         \begin{enumerate}
            \item In Section 2, I set out information with respect to Question 1 above;
            \item In Section 3, I set out information with respect to Question 2 above;
            \item In Section 4, I set out information with respect to Question 3 above;
         \end{enumerate}
     \item For convenience, I note that I have organised my findings in the same order as the questions outlined in my letter of instruction. I have also included questions, in some instances paraphrased, from the letter of instruction before presenting my corresponding findings. Additionally, I have referred to the appropriate section number as contained in the letter of instruction in my responses.
\end{myenum}
\label{sub:structure_of_this_report}

% subsection Structure of this report (end)

% section Introduction (end)

% paragraph  (end)
% section Background (end)
